\documentclass[10pt,a4paper,colorlinks,linkcolor=blue,urlcolor=blue]{moderncv}

%------------------------------------------------------------------------------
%                          STYLE AND COLOR
%------------------------------------------------------------------------------
\moderncvstyle{banking}  % 'casual', 'classic', 'oldstyle', or 'banking'
\moderncvcolor{darkmagenta}  % e.g., 'darkmagenta' for Durham, etc.
\usepackage[scale=0.78,a4paper]{geometry}
\usepackage{babel}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{lastpage}
\usepackage{footmisc} % for footnotes if needed
\usepackage[utf8]{inputenc}
\usepackage{fontawesome5}

\usepackage{textcomp}
\newcommand{\EUR}[1]{\texteuro{#1}}

%------------------------------------------------------------------------------
%                          PERSONAL DATA
%------------------------------------------------------------------------------
\name{Vatsal}{Sanjay}
\title{PhD}
\address{Department of Physics, Durham University}{PI, Computational Multiphase Physics Lab}{}
\email{vatsal.sanjay@comphy-lab.org}
\homepage{comphy-lab.org}
\social[github]{comphy-lab}

% (Optional) Include or remove your birthdate, updates, short lines, etc.
\extrainfo{Date of birth: Feb.~5, 1996 \quad Updated: \today}

%------------------------------------------------------------------------------
\begin{document}
\makecvtitle

%===============================
%         EDUCATION
%===============================
\section{Education}

\cventry{2018--2022}{Ph.D.~(Appl. Phys.)}{Physics of Fluids Dept.}{Univ.~Twente}{Graduated cum laude (with distinction)}{
  \textbf{Supervisor:} \href{https://en.wikipedia.org/wiki/Detlef_Lohse}{Prof.~Detlef Lohse}.\\
  \textbf{Thesis:} \emph{Viscous free-surface flows} (OA)~\href{https://doi.org/10.3990/1.9789036554077}{10.3990/1.9789036554077}.
}

\cventry{2013--2018}{B.Tech (Mech.) \& M.Tech (Thermal Eng.)}{Two-Phase Flow \& Instability Lab}{IIT Roorkee}{Graduated with distinction (Dept. Gold Medal)}{
  \textbf{Supervisor:} Prof.~Arup Kumar Das,\\
  \textbf{Thesis:}~\emph{Understanding of mutual interactions between liquid jets
  } (OA)~\href{http://dx.doi.org/10.13140/RG.2.2.22294.04166}{10.13140/RG.2.2.22294.04166}.
}

%===============================
%      PROFESSIONAL EXPERIENCE
%===============================
\section{Professional Experience}
\cventry{2025--present}{Assistant Professor}{Department of Physics}{Durham University}{PI of Computational Multiphase Physics (\href{https://comphy-lab.org}{CoMPhy}) Lab}{
  Leading research on multiphase flows and soft matter dynamics.
}
\cventry{2022--2025}{Postdoctoral Researcher}{Physics of Fluids Dept.}{Univ.~Twente}{Led Computational Multiphase Physics (\href{https://comphy-lab.org}{CoMPhy}) Lab}{
  Worked on non-Newtonian free-surface flows and soft matter singularities.
}
\cventry{May--July, 2016}{Research Intern}{Fluid Mechanics \& Acoustics Lab (UMR 5509)}{Univ.~Claude Bernard Lyon 1}{}{
  Worked on Landau--Levich dip coating (OA)~\href{https://doi.org/10.13140/RG.2.2.22076.91522}{10.13140/RG.2.2.22076.91522}.
}

\section{Major Awards \& Achievements}
\cvitem{2025}{\textbf{Ammodo Science Fellowship} \href{https://www.ammodo-science.org/researches/vatsal-sanjay}{\faPaperclip} -- To study mycofluidic transport.}
\cvitem{2024}{\textbf{J.~Fluid Mech.~Outstanding Reviewer} \href{https://www.cambridge.org/core/journals/journal-of-fluid-mechanics/announcements/prizes-and-awards/outstanding-reviewers-2023}{\faPaperclip} -- Top 1\% of reviewers in 2023.}
\cvitem{2024}{\textbf{KIVI Hoogendoorn Fluid Mechanics Award} \href{https://pof.tnw.utwente.nl/news/130}{\faPaperclip} -- Best PhD thesis in Netherlands (2022--2023).}
\cvitem{2024}{\textbf{Young Scientist} \href{https://www.knaw.nl/en/news/seven-young-scientists-attend-lindau-nobel-laureate-meetings}{\faPaperclip} -- 73rd Lindau Nobel Laureate Meeting (one of seven from Netherlands).}
\cvitem{2022}{\textbf{Doctor cum laude} -- Top 5\% of PhD graduates in 2021--2022.}
\cvitem{2018}{\textbf{Department Gold Medal} -- For academic excellence at IIT Roorkee.}
\cvitem{2015}{\textbf{Summer Undergraduate Research Award} -- To study bubble entrainment by impinging liquid jet.}

%===============================
%   SERVICE & REFEREEING
%===============================
\section{Service to the Community}

\cvitem{Seminars}{Physics of Fluids weekly seminar (2022--2025, avg.~40 participants, 10+ international speakers/yr).}
\cvitem{Conferences}{Symposium on Bubbles \& Bubbly Flows (2025, 75 participants), 35th Dutch Soft Matter Meeting (2024, 100 participants), Workshop on (De)Constructing Complex Contact Lines (2024, 25 participants).}
\cvitem{Referee}{J.~Fluid Mech.~(100+), Phys.~Rev. (20+), PNAS~(3), among others.}

\section{Research Funding}
\cvitem{2025}{\faLightbulb\hspace{0.2em}Ammodo Science Fellowship (\EUR{170000}) for Mycofluidic transport.}
\cvitem{2025}{\faServer\hspace{0.2em}30 million CPU hours (\EUR{450000} equivalent) on Snellius HPC (Co-PI).}
\cvitem{2023}{\faServer\hspace{0.2em}10 million CPU hours (\EUR{150000} equivalent) on Snellius HPC (Co-PI).}

\section{Scientific Outreach}
\cvitem{Outreach}{Social media manager for Physics of Fluids Dept. at \href{https://bsky.app/profile/poftwente.bsky.social}{BlueSky}\ \& \href{https://twitter.com/poftwente}{X}, APS-DFD mentor.}

\section{Supervision \& Teaching}
\cvitem{PhD}{4 students: J.~Talukdar (Singularities with surfactants, 2025-now), S.~Jana (Soft impacts, 2025-now), A.~Bhargava (Inertial contact lines, 2024-now), A.~Dixit (Non-Newtonian flows, 2023-now).}
\cvitem{Master}{8 theses: F.~Hoek (ongoing), S.~Jana (IIT KGP '25), J.~Talukdar (UT '25), V.~Rosario (UvA '24), S.~van~den~Heuvel (UT '23), C.H.~Maurits (UvA '23), T.~Appleford (UvA '22), S.~Meuleman (UT '20).}
\cvitem{Bachelor}{8 theses supervised at Univ. Twente (2019--2025).}
\cvitem{Teaching}{For teaching activities, see \href{https://comphy-lab.org/teaching/}{comphy-lab.org/teaching}.}


%===============================
%       PUBLICATIONS
%===============================
\section{Peer-Reviewed Publications}

\textbf{Recent publications} (20 total, 500+ citations):
\begin{enumerate}[leftmargin=1.5em,label=\textbf{[\arabic*]}]
\item Ç. Demirkır et al., \textbf{V. Sanjay}, et al., Jumping bubbles: adhesion and viscous dissipation, \textit{Phys. Rev. Fluids} 10, 123602 (2025).
\item J. Mclauchlan et al., \textbf{V. Sanjay}, et al., Bouncing microdroplets on hydrophobic surfaces, \textit{PNAS} 122, e2507309122 (2025).
\item M. Saini, \textbf{V. Sanjay}, et al., Integral surface tension formulations for Marangoni flows, \textit{J. Comput. Phys.} 542, 114348 (2025).
\item A. Bashkatov et al., \textbf{V. Sanjay}, et al., Electrolyte droplet spraying in H$_2$ bubbles, \textit{Nat. Commun.} 16, 4580 (2025).
\item A.K. Dixit et al., \textbf{V. Sanjay}, Viscoelastic Worthington jets, \textit{J. Fluid Mech.} 1010, A2 (2025).
\item \textbf{V. Sanjay} \& D. Lohse, Unifying theory of scaling in drop impact, \textit{Phys. Rev. Lett.} 134, 104003 (2025).
\item \textbf{V. Sanjay}, B. Zhang, et al., Viscosity role on drop impact forces, \textit{J. Fluid Mech.} 1004, A6 (2025); \textbf{Cover}.
\end{enumerate}

\textit{Full list:} \href{https://scholar.google.com/citations?user=tHb_qZoAAAAJ&hl=en}{Google Scholar}.

\section{Selected Talks}
\cvitem{Invited}{19 talks: WUR, Durham, DAMTP Cambridge, Univ.~Warwick, IIT Bombay, others.}
\cvitem{Contributed}{Selected talks: APS-DFD (5x), EFMC, EFDC, Liquid Matter Conf., ICR.}

\section{Metrics (as of \today)}
\begin{itemize}[leftmargin=1.5em]
\item \faIdCard\hspace{0.3em}\textbf{Researcher ID:} \href{https://www.webofscience.com/wos/author/record/K-1856-2019}{K-1856-2019}
\item \faOrcid\hspace{0.3em}\textbf{Orcid:} \href{https://orcid.org/0000-0002-4293-6099}{0000-0002-4293-6099}
\item \faChartLine\hspace{0.3em}\textbf{Hirsch-index:} H = 11 (\href{https://scholar.google.com/citations?hl=en&user=tHb_qZoAAAAJ}{Google Scholar}), 9 (\href{https://www.webofscience.com/wos/author/record/K-1856-2019}{Web of Science})
\item \faFile\hspace{0.3em}\textbf{i10-index:} 12 (\href{https://scholar.google.com/citations?hl=en&user=tHb_qZoAAAAJ}{Google Scholar})
\item \faUsers\hspace{0.3em}\textbf{Research Interest Score:} $1100+$ (top 2\% among \href{https://www.researchgate.net/profile/Vatsal-Sanjay-2}{ResearchGate} members who first published in 2015.)
\end{itemize}

\end{document}
