\documentclass[10pt,a4paper,colorlinks,linkcolor=blue,urlcolor=blue,citecolor=blue]{moderncv}

%------------------------------------------------------------------------------
%                          STYLE AND COLOR
%------------------------------------------------------------------------------
\moderncvstyle{banking}  % 'casual', 'classic', 'oldstyle', or 'banking'
\moderncvcolor{darkmagenta}  % e.g., 'darkmagenta' for Durham, etc.

\usepackage[scale=0.75,a4paper]{geometry}
\usepackage{babel}
\usepackage{xcolor}
\usepackage{enumitem}
\usepackage{amsmath}
\usepackage{lastpage}
\usepackage{footmisc} % for footnotes if needed
\usepackage[utf8]{inputenc}
\usepackage{fontawesome5}

\usepackage{textcomp}
\newcommand{\EUR}[1]{\texteuro{#1}}

%------------------------------------------------------------------------------
%                          PERSONAL DATA
%------------------------------------------------------------------------------
\name{Vatsal}{Sanjay}
\title{PhD}
\address{Department of Physics, Durham University}{PI, Computational Multiphase Physics Lab}{}
\email{vatsal.sanjay@comphy-lab.org}
\homepage{comphy-lab.org}
\social[github]{comphy-lab}

% (Optional) Include or remove your birthdate, updates, short lines, etc.
\extrainfo{Date of birth: Feb.~5, 1996 \quad Updated: \today}

%------------------------------------------------------------------------------
\begin{document}
\makecvtitle

%------------------------------------------------------------------------------
% NOTE TO SELF (SUGGESTED):
%  I have removed older lines in "Education" like high-school details or
%  older achievements if you want a tight academic CV. I've left them in for as comments. Just in case!

%===============================
%         EDUCATION
%===============================
\section{Education}

\cventry{2018--2022}{Ph.D.~(Appl. Phys.)}{Physics of Fluids Dept.}{Univ.~Twente}{Graduated cum laude (with distinction)}{
  \textbf{Supervisor:} \href{https://en.wikipedia.org/wiki/Detlef_Lohse}{Prof.~Detlef Lohse}.\\
  \textbf{Thesis:} \emph{Viscous free-surface flows} (OA)~\href{https://doi.org/10.3990/1.9789036554077}{10.3990/1.9789036554077}.
}

\cventry{2013--2018}{B.Tech (Mech.) \& M.Tech (Thermal Eng.)}{Two-Phase Flow \& Instability Lab}{IIT Roorkee}{Graduated with distinction (Dept. Gold Medal)}{
  \textbf{Supervisor:} Prof.~Arup Kumar Das,\\
  \textbf{Thesis:}~\emph{Understanding of mutual interactions between liquid jets %: Entrainment and sheet formation
  } (OA)~\href{http://dx.doi.org/10.13140/RG.2.2.22294.04166}{10.13140/RG.2.2.22294.04166}.
}
%\cventry{\textbf{2013}}{High School (AISSCE)}{}{}{}{}
%\cvitem{Graduated}{First Division with \textit{96.4\%} marks.}
%\cventry{\textbf{2011}}{AISSE}{Secondary School}{Graduated with CGPA of \textit{10/10}}{}{}

%===============================
%      PROFESSIONAL EXPERIENCE
%===============================
\section{Professional Experience}
\cventry{2025--present}{\textbf{Assistant Professor}}{Department of Physics}{Durham University}{PI of Computational Multiphase Physics (\href{https://comphy-lab.org}{CoMPhy}) Lab}{
  Leading research on multiphase flows and soft matter dynamics.
}
\cventry{2022--2025}{\textbf{Postdoctoral Researcher}}{Physics of Fluids Dept.}{Univ.~Twente}{Led Computational Multiphase Physics (\href{https://comphy-lab.org}{CoMPhy}) Lab}{
  Worked on non-Newtonian free-surface flows and soft matter singularities.
}
\cventry{May--July, 2016}{\textbf{Research Intern}}{Fluid Mechanics \& Acoustics Lab (UMR 5509)}{Univ.~Claude Bernard Lyon 1}{}{
  Worked on Landau--Levich dip coating (OA)~\href{https://doi.org/10.13140/RG.2.2.22076.91522}{10.13140/RG.2.2.22076.91522}.
}

%===============================
%      AWARDS & HONORS
%===============================
\section{Major Awards \& Achievements}

\cventry{2025}{\textbf{Ammodo Science Fellowship} \href{https://www.ammodo-science.org/researches/vatsal-sanjay}{\faPaperclip}}{}{}{}{
  To study mycofluidic transport.
}

\cventry{2024}{\textbf{J.~Fluid Mech.~Outstanding Reviewer} \href{https://www.cambridge.org/core/journals/journal-of-fluid-mechanics/announcements/prizes-and-awards/outstanding-reviewers-2023}{\faPaperclip}}{}{}{}{
  Top 1\% of reviewers in 2023.
}

\cventry{2024}{\textbf{KIVI Hoogendoorn Fluid Mechanics Award} \href{https://pof.tnw.utwente.nl/news/130}{\faPaperclip}}{}{}{}{
  Best PhD thesis in NL (2022--2023).
}

\cventry{2024}{\textbf{Young Scientist} \href{https://www.knaw.nl/en/news/seven-young-scientists-attend-lindau-nobel-laureate-meetings}{\faPaperclip}}{}{}{nominated by KNAW}{
  73rd Lindau Nobel Laureate Meeting (one of seven from NL).
}
\cventry{2022}{\textbf{Doctor cum laude}}{}{}{met lof (with distinction)}{
  Top 5\% of PhD graduates in 2021--2022.
}
\cventry{2018}{\textbf{Department Gold Medal}}{}{}{}{
  For academic excellence at IIT Roorkee.
}
\cventry{2015}{\textbf{Summer Undergraduate Research Award}}{}{}{}{
  To study bubble entrainment by impinging liquid jet.
}

%===============================
%   SERVICE & REFEREEING
%===============================
\section{Service to the Community}

\subsection{\faUsers\hspace{0.3em}Seminars \& Conferences}

\cventry{2022--2025}{avg.~40 participants, 10+ international speakers/yr}{Physics of Fluids weekly seminar}{Univ.~Twente}{\href{https://pof.tnw.utwente.nl/agenda}{link}}{}

\cventry{May 2025}{75 participants}{Symposium on \textit{Bubbles \& Bubbly Flows}}{Univ.~Twente}{}{}

\cventry{Jun 2024}{25 participants}{Workshop on \textit{(De)Constructing Complex Contact Lines}}{Lorentz Center}{\href{https://www.lorentzcenter.nl/deconstructing-complex-contact-lines.html}{link}}{}

\cventry{May 2024}{100 participants; received NWO Meetings Grant}{\textit{35th Dutch Soft Matter Meeting}}{Univ.~Twente}{}{}

\cventry{Oct 2023}{200 participants}{Flow for Future conference: 25 years of Physics of Fluids}{Univ.~Twente}{}{}

\subsection{\faCheck\hspace{0.3em}Refereeing}
\cvitem{2018--}{J.~Fluid Mech.~(100+), Phys.~Rev.~(20+), PNAS~(3), among others.}

%===============================
%      RESEARCH FUNDING
%===============================
\section{Research Funding}
\cvitem{2025}{\faLightbulb\hspace{0.2em}Ammodo Science Fellowship (\EUR{170000}) for Mycofluidic transport. \href{https://www.ammodo-science.org/researches/vatsal-sanjay}{\faPaperclip}}
\cvitem{2025}{\faServer\hspace{0.2em}30 million CPU hours (\EUR{450000} equivalent) on Snellius HPC (Co-PI).}
\cvitem{2023}{\faServer\hspace{0.2em}10 million CPU hours (\EUR{150000} equivalent) on Snellius HPC (Co-PI).}

%===============================
%   SCIENTIFIC OUTREACH
%===============================
\section{Scientific Outreach}
\cvitem{2020--2025}{Social media manager for Physics of Fluids Dept. at \href{https://bsky.app/profile/poftwente.bsky.social}{BlueSky}\ \& \href{https://twitter.com/poftwente}{X}.}
\cvitem{2022--}{APS-DFD peer mentoring (mentor).}
\cvitem{2022--}{Skype a Scientist (high-school outreach).}
\cvitem{2022--2023}{Physicist To-Go (APS).}
\cvitem{2021}{Panel discussion on \emph{Future of Fluid Dynamics}.}
\cvitem{2021}{Panel discussion on \emph{Research \& Higher Education}. \href{https://youtu.be/dorx1L8G0D0?si=5UqSRgPWrZzKEt-h}{\color{red}\faYoutube}}

%===============================
%  SUPERVISION & TEACHING
%===============================
\section{Supervision}

\subsection{\faUserGraduate\hspace{0.3em}PhD Theses}
\cvitem{J.~Talukdar}{Singularities with surfactants (since Jul.~2025).}
\cvitem{S.~Jana}{Soft impacts (since Jun.~2025).}
\cvitem{A.~Bhargava}{Inertial contact lines (since Jan.~2024).}
\cvitem{A.~Dixit}{Non-Newtonian flows (since Jul.~2023).}

\subsection{\faGraduationCap\hspace{0.3em}Master Theses}
\cvitem{}{F.~Hoek (UT, ongoing), S.~Jana (IIT KGP, '25, \href{https://bit.ly/ThesisJana}{\faGraduationCap}), J.~Talukdar (UT, '25, \href{https://bit.ly/thesisJnan}{\faGraduationCap}),
V.~Rosario (UvA, '24, \href{https://bit.ly/thesisRosario}{\faGraduationCap}),
S.~van~den~Heuvel (UT, '23, \href{https://bit.ly/thesisSwen}{\faGraduationCap}),
C.H.~Maurits (UvA, '23, \href{https://bit.ly/ThesisLuuk}{\faGraduationCap}),
T.~Appleford (UvA, '22, \href{https://bit.ly/ThesisTom}{\faGraduationCap}),
S.~Meuleman (UT, '20, \href{https://bit.ly/thesisMeuleman}{\faGraduationCap}).}

\subsection{\faUniversity\hspace{0.3em}Bachelor Theses}
\cvitem{}{M.~Sent (UT, '25, \href{https://bit.ly/thesisSent}{\faGraduationCap}), N.~Kuipers (UT, '23, \href{https://bit.ly/thesisKuipers}{\faGraduationCap}), J.~Talukdar (UT, '23),
T.~Heijink (UT, '21, \href{https://bit.ly/ThesisTwanHeijink}{\faGraduationCap}), T.~Kroeze (UT, '20, \href{https://bit.ly/ThesisThijmenKroeze}{\faGraduationCap}),
C.~Verschuur (UT, '20, \href{https://bit.ly/ThesisCoenVerschuur}{\faGraduationCap}),
P.J.~Dekker (UT, '19, \href{https://bit.ly/ThesisPimDekker}{\faGraduationCap}),
L.~Bruggink (UT, '19, \href{https://bit.ly/ThesisLaurenceBruggink}{\faGraduationCap}).}

\section{Teaching}
\cventry{2025--}{Lecturer}{Introduction to Soft Matter}{Durham University}{}{Course notes available at \href{https://blogs.comphy-lab.org/Lecture-Notes/Intro-Soft-Matter/0-README}{blogs.comphy-lab.org}.}
\cventry{Mar 10--13, 2025}{Instructor}{High-Fidelity Simulations Using Basilisk C}{Universidad Carlos III de Madrid, ES}{}{4-day interactive course on computational fluid dynamics. Also available as self-paced course at \href{https://comphy-lab.org/teaching/2025-Basilisk101-Madrid}{comphy-lab.org}.}
\cventry{2018--2025}{Co-lecturer}{Advanced Fluid Mechanics}{Univ.~Twente}{}{}
\cvitem{}{For complete teaching activities, visit \href{https://comphy-lab.org/teaching/}{comphy-lab.org/teaching}.}

%===============================
%       PUBLICATIONS
%===============================
\section{Peer-Reviewed Publications}
% SUGGESTION: If you want to highlight only 5 or so selected publications, rename
% the section "Selected Publications," list them, then say "Full list at ..."

\begin{enumerate}[leftmargin=1.5em,label=\textbf{[\arabic*]}]
	\item Çayan Demirkır, Rui Yang, Aleksandr Bashkatov, \textbf{Vatsal Sanjay}, Detlef Lohse, and Dominik Krug,\\
	To jump or not to jump: Adhesion and viscous dissipation dictate the detachment of coalescing wall-attached bubbles,\\
	Phys. Rev. Fluids, 10(12), 123602 (2025) [15 pages];\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.1103/PhysRevFluids.10.123602}{10.1103/PhysRevFluids.10.123602};\\
	\faGithub\hspace{0.2em}\href{https://github.com/VatsalSy/jumping-bubbles}{Repository}.

	\item Josephine Mclauchlan, Jessica S. Walker, \textbf{Vatsal Sanjay}, Maziyar Jalaal, Jonathan P. Reid, Adam M. Squires, and Anton Souslov,\\
	Bouncing microdroplets on hydrophobic surfaces,\\
	PNAS, 122, e2507309122 (2025) [8 pages];\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.1073/pnas.2507309122}{10.1073/pnas.2507309122}.

	\item Mandeep Saini, \textbf{Vatsal Sanjay}, Youssef Saade, Detlef Lohse, and Stéphane Popinet,\\
	Implementation of integral surface tension formulations in a volume of fluid framework and their applications to Marangoni flows,\\
	J. Comput. Phys., 542, 114348 (2025) [20 pages];\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.1016/j.jcp.2025.114348}{10.1016/j.jcp.2025.114348};\\
	\faGithub\hspace{0.2em}\href{https://github.com/comphy-lab/marangoniSheet}{Repository}.

	\item Aleksandr Bashkatov, Florian Bürkle, Çayan Demirkır, Wei Ding, \textbf{Vatsal Sanjay}, Alexander Babich, Xuegeng Yang, Gerd Mutschke, Jürgen Czarske, Detlef Lohse, Dominik Krug, Lars Büttner, and Kerstin Eckert,\\
	Electrolyte droplet spraying in H$_2$ bubbles during water electrolysis under normal and microgravity conditions,\\
	Nat. Commun., 16, 4580 (2025) [10 pages];\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.1038/s41467-025-59762-7}{10.1038/s41467-025-59762-7};\\
	\faGithub\hspace{0.2em}\href{https://github.com/VatsalSy/Asymmetries-in-coalescence}{Repository}.

	\item Ayush K. Dixit, Alexandros T. Oratis, Konstantinos Zinelis, Detlef Lohse, and \textbf{Vatsal Sanjay},\\
	Viscoelastic Worthington jets and droplets produced by bursting bubbles,\\
	J. Fluid Mech., 1010, A2 (2025) [32 pages];\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.1017/jfm.2025.237}{10.1017/jfm.2025.237};\\
	\faGithub\hspace{0.2em}\href{https://github.com/comphy-lab/Viscoelastic-Worthington-jets-and-droplets-produced-by-bursting-bubbles}{Repository}.

	\item \textbf{Vatsal Sanjay} and Detlef Lohse,\\
	Unifying theory of scaling in drop impact: Forces \& maximum spreading diameter,\\
	Phys. Rev. Lett., 134, 104003 (2025) [9 pages];\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.1103/PhysRevLett.134.104003}{10.1103/PhysRevLett.134.104003};\\
	\faGithub\hspace{0.2em}\href{https://github.com/comphy-lab/Drop-Impact}{Repository}.

	\item \textbf{Vatsal Sanjay}, Bin Zhang, Cunjing Lv, and Detlef Lohse,\\
	The role of viscosity on drop impact forces on non-wetting surfaces,\\
	J. Fluid Mech., 1004, A6 (2025) [23 pages];\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.1017/jfm.2024.982}{10.1017/jfm.2024.982};\\
	\faStar\hspace{0.2em}\textbf{Cover} of that volume of J. Fluid Mech.;\\
	\faGithub\hspace{0.2em}\href{https://github.com/VatsalSy/The-role-of-viscosity-on-drop-impact-forces}{Repository}.

	\item Lohit Kayal, \textbf{Vatsal Sanjay}, Nikhil Yewale, Anil Kumar, and Ratul Dasgupta,\\
	Focusing of concentric free-surface waves,\\
	J. Fluid Mech., 1003, A14 (2025) [39 pages];\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.1017/jfm.2024.1089}{10.1017/jfm.2024.1089};\\
	\faGithub\hspace{0.2em}\href{https://github.com/comphy-lab/concentricWave}{Repository}.

	\item Arivazhagan G. Balasubramanian, \textbf{Vatsal Sanjay}, Maziyar Jalaal, Ricardo Vinuesa, and Outi Tammisola,\\
	Bursting bubble in an elasto-viscoplastic medium,\\
	J. Fluid Mech., 1001, A9 (2024) [36 pages];\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.1017/jfm.2024.1073}{10.1017/jfm.2024.1073};\\
	\faStar\hspace{0.2em}\textbf{Cover} of that volume of J. Fluid Mech.;\\
	\faGithub\hspace{0.2em}\href{https://github.com/comphy-lab/2023_Bubble-bursting-in-an-elasto-viscoplastic-medium}{Repository}.

	\item \textbf{Vatsal Sanjay}, Pierre Chantelot, and Detlef Lohse,\\
	When does an impacting drop stop bouncing?,\\
	J. Fluid Mech., 958, A26 (2023) [20 pages];\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.1017/jfm.2023.55}{10.1017/jfm.2023.55};\\
	\faGithub\hspace{0.2em}\href{https://github.com/comphy-lab/Drop-Impact}{Repository}.

	\item \textbf{Vatsal Sanjay}, Srinath Lakshman, Pierre Chantelot, Jacco H. Snoeijer, and Detlef Lohse,\\
	Drop impact on viscous liquid films,\\
	J. Fluid Mech., 958, A25 (2023) [28 pages];\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.1017/jfm.2023.13}{10.1017/jfm.2023.13};\\
	\faGithub\hspace{0.2em}\href{https://github.com/VatsalSy/Drop-impact-on-viscous-liquid-films}{Repository}.

	\item Bin Zhang, \textbf{Vatsal Sanjay}, Songlin Shi,  Yinggang Zhao,  Cunjing Lv,  Xi-Qiao Feng,  and Detlef Lohse,\\
	Impact forces of water drops falling on superhydrophobic surfaces,\\
	Phys. Rev. Lett. 129, 104501 (2022) [7 pages],\\
	\faLock\hspace{0.2em}DOI: \href{https://doi.org/10.1103/PhysRevLett.129.104501}{10.1103/PhysRevLett.129.104501}, \faFile\hspace{0.2em}OA:  \href{https://doi.org/10.48550/arXiv.2202.02437}{10.48550/arXiv.2202.02437};\\
	see also
	\begin{itemize}
		\item
		\faChartLine\hspace{0.2em}As of March/April 2024, this \textit{highly cited paper} received enough citations to place it in the top 1\% of the academic field of Physics based on a highly cited threshold for the field and publication year. Source: Web of Science.
		\item
		\faStar\hspace{0.2em}Editor's Suggestion of that issue.
		\item
		Davide Castelvecchi, Research Highlight: ``The physics of a bouncing droplet's impact'', \href{https://www.nature.com/articles/d41586-022-02302-w}{Nature, article: d41586-022-02302-w} (29/8/2022)
		\item
		\faGithub\hspace{0.2em}\href{https://github.com/VatsalSy/Impact-forces-of-water-drops-falling-on-superhydrophobic-surfaces}{Repository}.
	\end{itemize}

	\item \textbf{Vatsal Sanjay}, Uddalok Sen, Pallav Kant, and Detlef Lohse,\\
	Taylor-Culick retractions and the influence of the surroundings,\\
	J. Fluid Mech. 948, A14  (2022) [37 pages];\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.1017/jfm.2022.671}{10.1017/jfm.2022.671};\\
	\faGithub\hspace{0.2em}\href{https://github.com/VatsalSy/Taylor-Culick-retractions}{Repository}.

	\item \textbf{Vatsal Sanjay}, Detlef Lohse, and Maziyar Jalaal,\\
	Bursting bubble in a viscoplastic medium,\\
	J. Fluid Mech. 922, A22  (2021) [24 pages];\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.1017/jfm.2021.489}{10.1017/jfm.2021.489};\\
	\faGithub\hspace{0.2em}\href{https://github.com/VatsalSy/Bursting-Bubble-In-a-Viscoplastic-Medium}{Repository}.

	\item Olinka Ramirez-Soto, \textbf{Vatsal Sanjay},  Detlef Lohse,  Jonathan T. Pham, and Doris Vollmer,\\
	Lifting a sessile oil drop with an impacting one,\\
	Sci. Adv. 6, eaba4330  (2020) [11 pages];\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.1126/sciadv.aba4330}{10.1126/sciadv.aba4330};\\
	\faGithub\hspace{0.2em}\href{https://github.com/VatsalSy/Lifting-a-sessile-drop}{Repository}.

	\item Abhinav Jain, \textbf{Vatsal Sanjay}, and Arup Kumar Das,\\
	Consequences of inclined and dual jet impingement in stagnant liquid and stratified layers,\\
	AlChE J. 65(1), 372-384  (2019) [12 pages],\\
	\faLock\hspace{0.2em}DOI: \href{https://doi.org/10.1002/aic.16373}{10.1002/aic.16373}, \faFile\hspace{0.2em}OA: \href{https://tinyurl.com/24p5dy8s}{archived pdf}.

	\item Anurag Soni, \textbf{Vatsal Sanjay}, and Arup Kumar Das,\\
	Formation of fluid structures due to jet-jet and jet-sheet interactions,\\
	Chem. Eng. Sci. 191, 67-77  (2018) [11 pages],\\
	\faLock\hspace{0.2em}DOI: \href{https://doi.org/10.1016/j.ces.2018.06.055}{10.1016/j.ces.2018.06.055}, \faFile\hspace{0.2em}OA: \href{https://tinyurl.com/2bv5fznd}{archived pdf}.

	\item \textbf{Vatsal Sanjay} and Arup Kumar Das,\\
	Numerical assessment of hazard in compartmental fire having steady heat release rate from the source,\\
	Build. Simul. 11(3), 613-624  (2018) [12 pages],\\
	\faLock\hspace{0.2em}DOI: \href{https://doi.org/10.1007/s12273-017-0411-y}{10.1007/s12273-017-0411-y}, \faFile\hspace{0.2em}OA: \href{https://tinyurl.com/2bwhzlzv}{archived pdf}.

	\item \textbf{Vatsal Sanjay} and Arup Kumar Das,\\
	On air entrainment in a water pool by impingement of a jet,\\
	AIChE J. 63(11), 5169--5181  (2017) [23 pages],\\
	\faLock\hspace{0.2em}DOI: \href{https://doi.org/10.1002/aic.15828}{10.1002/aic.15828}, \faFile\hspace{0.2em}OA: \href{https://tinyurl.com/24ne4oql}{archived pdf}.

	\item \textbf{Vatsal Sanjay} and Arup Kumar Das,\\
	Formation of liquid chain by collision of two laminar jets,\\
	Phys. Fluids 29, 112101  (2017) [12 pages];\\
	\faLock\hspace{0.2em}DOI: \href{https://doi.org/10.1063/1.4998288}{10.1063/1.4998288}, \faFile\hspace{0.2em}OA: \href{https://tinyurl.com/27sd7lgo}{archived pdf};\\
	\faGithub\hspace{0.2em}\href{https://github.com/VatsalSy/FluidChains}{Repository}.

\end{enumerate}

%===============================
%    WORKS UNDER REVIEW
%===============================
\section{Works Under Review / In Preparation}
\begin{enumerate}[leftmargin=1.5em,label=\textbf{[\arabic*]}]
	\item Amir H. Ghaemi, Zhengyu Yang, A. Huang, \textbf{Vatsal Sanjay}, Jie Feng, and C. Ricardo Constante-Amores,\\
	Bursting Bubbles in Herschel-Bulkley Fluids: Dynamics and Jetting Transitions,\\
	arXiv preprint,\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.48550/arXiv.2511.23345}{10.48550/arXiv.2511.23345};\\
	\faGithub\hspace{0.2em}\href{https://github.com/comphy-lab/BurstingBubble_Herschel-Bulkley}{Repository}.

	\item Diego Díaz, Anvesh Bhargava, Florian Walz, Azadeh Sharifi, Saravanan Sumally, Rüdiger Berger, Michael Kappl, Hans-Jürgen Butt, Detlef Lohse, Tim Willers, \textbf{Vatsal Sanjay}, and Doris Vollmer,\\
	Stood-up drop to measure receding contact angles,\\
	arXiv preprint,\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.48550/arXiv.2511.20259}{10.48550/arXiv.2511.20259};\\
	\faGithub\hspace{0.2em}\href{https://github.com/comphy-lab/Retracting-Droplet}{Repository}.

	\item Coen I. Verschuur, Alexandros T. Oratis, \textbf{Vatsal Sanjay}, and Jacco H. Snoeijer,\\
	How elasticity affects bubble pinch-off,\\
	arXiv preprint,\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.48550/arXiv.2511.20075}{10.48550/arXiv.2511.20075};\\
	\faGithub\hspace{0.2em}\href{https://github.com/comphy-lab/ElasticPinchOff}{Repository}.

	\item Ayush K. Dixit, Chenglong Zhao, Stéphane Zaleski, Detlef Lohse, and \textbf{Vatsal Sanjay},\\
	Holey sheets: double-threshold rupture of draining liquid films,\\
	arXiv preprint,\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.48550/arXiv.2509.12789}{10.48550/arXiv.2509.12789};\\
	\faGithub\hspace{0.2em}\href{https://github.com/comphy-lab/HoleySheet}{Repository}.

	\item Saumili Jana, John Kolinski, Detlef Lohse, and \textbf{Vatsal Sanjay},\\
	Impacting spheres: from liquid drops to elastic beads,\\
	arXiv preprint,\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.48550/arXiv.2510.24855}{10.48550/arXiv.2510.24855};\\
	\faGithub\hspace{0.2em}\href{https://github.com/comphy-lab/Soft-Sphere-Impacts}{Repository}.

	\item Tom Appleford, \textbf{Vatsal Sanjay}, and Maziyar Jalaal,\\
	On the Rheology of Two-Dimensional Dilute Emulsions,\\
	arXiv preprint,\\
	\faFile\hspace{0.2em}DOI: \href{https://doi.org/10.48550/arXiv.2508.13022}{10.48550/arXiv.2508.13022};\\
	\faGithub\hspace{0.2em}\href{https://github.com/tappleford/droplet_under_shear_newtonian_2D}{Repository}.

	\item \textbf{Vatsal Sanjay}, Aleksandr Bashkatov, Çayan Demirkır, Kerstin Eckert, Dominik Krug, and Detlef Lohse,\\
	Worthington jet injects droplets during coalescence of asymmetric bubbles,\\
	to be submitted to J. Fluid Mech., \href{https://youtu.be/WZonMHzzkXQ}{click here for results};\\
	\faGithub\hspace{0.2em}\href{https://github.com/VatsalSy/Asymmetries-in-coalescence}{Repository}.

	\item Vincent Bertin, \textbf{Vatsal Sanjay}, Charu Datt, Alexandros T. Oratis, Jacco H. Snoeijer,\\
	Elastic Taylor-Culick retraction,\\
	to be submitted to Phys. Rev. Lett., \href{https://tinyurl.com/2cvo89bd}{click here for results}.

	\item Jnandeep Talukdar, Uddalok Sen, Christian Diddens, Detlef Lohse, \textbf{Vatsal Sanjay},\\
	Sliding drops on dry \& wet substrates,\\
	to be submitted to Phys. Rev. Fluids, \href{https://tinyurl.com/2xvlhlc6}{click here for results}.

\end{enumerate}

%===============================
%      SELECTED TALKS
%===============================
\section{Invited \& Contributed Talks}

\subsection{\faMicrophone\hspace{0.3em}Invited Talks}
\begin{itemize}[leftmargin=1.5em]
\item[\textbullet] (Oct.~24, 25) \emph{Sheets \& Bioaerosols: Computational Multiphase Physics for the Life Sciences} \\
  Lunchtime Seminar, Biophysical Science Institute, Durham University, UK.
\item[\textbullet] (Oct.~17, 25) \emph{Can polymeric flow be the Drosophila of unsteady continuum mechanics?} \\
  Dept.~Mathematics, Imperial College London, UK.
\item[\textbullet] (Jun.~16, 25) \emph{Impacting spheres: from viscous drops to elastic beads} \\
  Univ.~Warwick, UK.
\item[\textbullet] (Jun.~11, 25) \emph{So long, and thanks for all the flow} \\
  Univ.~Twente, NL.
\item[\textbullet] (Apr.~1, 25) \emph{Hydrodynamic singularities in soft matter flows} \\
  Wageningen University \& Research (WUR), NL.
\item[\textbullet] (Mar.~20, 25) \emph{Can polymeric flows be the Drosophila of continuum mechanics?} \\
  Condensed Matter Physics Seminar Series, Durham University, UK.
\item[\textbullet] (Jan.~30, 25) \emph{Can polymeric flows be the Drosophila of unsteady continuum mechanics?} \\
  Univ.~Illinois at Urbana-Champaign, USA (Virtual).
\item[\textbullet] (Jan.~20, 25) \emph{Hydrodynamic singularities in soft matter flows} \\
  DAMTP, Univ.~Cambridge, UK.
\item[\textbullet] (Jan.~6, 25) \emph{Can polymeric flows be the Drosophila of unsteady continuum mechanics?}\\
  Chaotic Flows in Polymer Solutions workshop, Univ.~Edinburgh, UK.
\item[\textbullet] (Oct.~9, 24) \emph{Hydrodynamic singularities in soft matter flows} \\
  Univ.~Warwick, UK.
\item[\textbullet] (May~30, 24) \emph{Viscous free-surface flows} \\
  Burgers Symposium, NL.
\item[\textbullet] (Apr.~12, 24) \emph{Soft matter singularities} \\
  Univ.~Edinburgh, UK.
\item[\textbullet] (Mar.~4, 24) \emph{Deformable soft matter} \\
  Dynamics of Interfaces, Univ.~Augsburg, DE.
\item[\textbullet] (Jan.~20, 23) \emph{Impact of droplets} \\
  Univ.~Claude Bernard Lyon 1, FR.
\item[\textbullet] (Jan.~10, 23) \emph{Impact of droplets} \\
  IIT Delhi, IN.
\item[\textbullet] (Jan.~4, 23) \emph{Impact of droplets} \\
  IIT Patna, IN.
\item[\textbullet] (Dec.~26, 22) \emph{Taylor-Culick retractions} \\
  IIT Kharagpur, IN.
\item[\textbullet] (Dec.~12, 22) \emph{Taylor-Culick retractions} \\
  IIT Roorkee, IN.
\item[\textbullet] (Dec.~7, 22) \emph{Drop impact forces} \\
  IIT Bombay, IN.
\item[\textbullet] (Oct.~26, 22) \emph{Drop impact forces} \\
  CFSM Seminar Series, USA (Virtual). \href{https://www.youtube.com/live/enTMAucwUDs?si=Dm-IJ3A0o7AhMc2T}{\color{red}\faYoutube}
\item[\textbullet] (Oct.~12, 22) \emph{Drop impact forces} \\
  Univ.~Akron, USA (Virtual).
\item[\textbullet] (Jul.~10, 22) \emph{Precursor films help simulate three-phase flows} \\
  Physics of Fluids Soft Matter Seminar, Univ.~Twente, NL. \href{https://youtu.be/ozrnYe8u1HA?si=DA4JIFjNozmPsQuE}{\color{red}\faYoutube}
\item[\textbullet] (Jan.~8, 18) \emph{Formation of liquid chain by collision of two laminar jets} \\
  Univ.~Twente, NL.
\item[\textbullet] (Mar.~27, 17) \emph{Understanding of mutual interactions between liquid jets\ldots} \\
  Cognizance Fest, IIT Roorkee, IN.
\end{itemize}

\subsection{\faComments\hspace{0.3em}Selected Contributed Talks}
\begin{itemize}[leftmargin=1.5em]
\item[\textbullet] (Nov.~25) \emph{Sessile drop coalescence with surfactants}, APS-DFD, Houston, USA.
\item[\textbullet] (Jul.~25) \emph{Can polymeric flows be the Drosophila of unsteady continuum mechanics?}, Basilisk/Gerris Meeting, Oxford, UK.
\item[\textbullet] (Jun.~25) \emph{Taming singularities: yield-stress regularization in bubble bursting}, VPF10, Amsterdam, NL.
\item[\textbullet] (Nov.~24) \emph{Dissipative anomaly in sliding drops}, APS-DFD, Salt Lake City, USA.
\item[\textbullet] (Sep.~24) \emph{Drop Impact Forces}, 12th Liquid Matter Conf., Mainz, DE.
\item[\textbullet] (Sep.~24) \emph{A unifying approach for drop impact dynamics on rigid surfaces}, 1st EFDC, Aachen, DE.
\item[\textbullet] (Apr.~24) \emph{Bursting bubbles in a viscoelastic medium}, European Rheology Conf., Leeds, UK.
\item[\textbullet] (Nov.~23) \emph{A unifying approach for droplet impact forces}, APS-DFD, Washington, DC, USA. \href{https://youtu.be/3S_hwkMCx6U?si=01tvC4RHCoga62bC}{\color{red}\faYoutube}
\item[\textbullet] (Nov.~22) \emph{Impact forces of water drops.}, APS-DFD, Indianapolis, USA. \href{https://youtu.be/U0g67zV70hw}{\color{red}\faYoutube}
\item[\textbullet] (Jul.~23) \emph{Viscous free-surface flows}, Basilisk/Gerris Meeting, Paris, FR.
\item[\textbullet] (Sep.~22) \emph{When does an impacting drop stop bouncing?}, EFMC14, Athens, GR.
\item[\textbullet] (Jan.~22) \emph{How much force is required to play ping-pong with water droplets?}, Physics@Veldhoven, NL. \href{https://youtu.be/wmEYeQRPi0Q?si=u8Ex64dYLHQ8TxCE}{\color{red}\faYoutube}
\item[\textbullet] (Nov.~21) \emph{Viscous dissipation dictates Taylor-Culick type retractions}, APS-DFD, Phoenix, USA. \href{https://youtu.be/d0tMlpbMIqY?si=V-7Lh5g-zj1j7al6}{\color{red}\faYoutube}
\item[\textbullet] (Dec.~20) \emph{Bursting Bubble in a Viscoplastic medium}, International Congress on Rheology (Virtual). \href{https://youtu.be/52D6nfaHbYg?si=lE3oQGiMZe3UCT6j}{\color{red}\faYoutube}
\item[\textbullet] (Nov.~20) \emph{When does a viscous drop stop bouncing?}, APS-DFD (Virtual). \href{https://youtu.be/9JCV9JFwr2A?si=Vs1ljwdmZrzHUOXX}{\color{red}\faYoutube}
\item[\textbullet] (Feb.~20) \emph{Jumping \& Bouncing Drops \& Bubbles}, Max Planck meeting, Mainz, DE.
\item[\textbullet] (Nov.~19) \emph{Droplet Encapsulation}, APS-DFD, Seattle, USA.
\item[\textbullet] (Sep.~19) \emph{Bursting Bubbles: from Champagne to Mudpots}, VPF8, Cambridge, UK.
\item[\textbullet] (Aug.~19) \emph{Impinging drop lifts a sessile drop}, 9th 4U Summer School, DK.
\item[\textbullet] (May~16) \emph{On gas-liquid entrainment by impinging jet}, ICMF9, Florence, IT.
\end{itemize}

%===============================
%       SUMMARY / METRICS
%===============================
\section{Summary of Key Numbers (as of \today)}
\begin{itemize}[leftmargin=1.5em]
\item \faIdCard\hspace{0.3em}\textbf{Researcher ID:} \href{https://www.webofscience.com/wos/author/record/K-1856-2019}{K-1856-2019}
\item \faOrcid\hspace{0.3em}\textbf{Orcid:} \href{https://orcid.org/0000-0002-4293-6099}{0000-0002-4293-6099}
\item \faChartLine\hspace{0.3em}\textbf{Hirsch-index:} H = 11 (\href{https://scholar.google.com/citations?hl=en&user=tHb_qZoAAAAJ}{Google Scholar}), 9 (\href{https://www.webofscience.com/wos/author/record/K-1856-2019}{Web of Science})
\item \faFile\hspace{0.3em}\textbf{i10-index:} 12 (\href{https://scholar.google.com/citations?hl=en&user=tHb_qZoAAAAJ}{Google Scholar})
\item \faUsers\hspace{0.3em}\textbf{Research Interest Score:} \(1100+\) (top 2\% among \href{https://www.researchgate.net/profile/Vatsal-Sanjay-2}{ResearchGate} members who first published in 2015.)
\end{itemize}

% %------------------------------------------------------------------------------
% % POSSIBLE SUGGESTION:
% %  For a truly short CV (2-3 pages), you can move "Older contributed talks" or
% %  "Full publications list" to your personal website (and keep just a selection).
% %------------------------------------------------------------------------------

\end{document}
