\documentclass[11pt,a4paper,roman,english,colorlinks,linkcolor=true]{moderncv}
\moderncvstyle{classic}%'casual', 'classic', 'oldstyle' and 'banking'
\moderncvcolor{red}%'blue', 'orange', 'green', 'red', 'purple', 'grey' and 'black'
\usepackage[utf8]{inputenc}
\usepackage[scale=0.75,a4paper]{geometry}
\usepackage{babel}
\usepackage{xcolor}
\usepackage[url=false,
backend=bibtex,
style=numeric,
doi=true,
isbn=true,
backref=false,
maxnames=99,
defernumbers=true,
natbib=true,
sorting=ydnt]{biblatex}

\addbibresource{publications/journal2023.bib}
\addbibresource{publications/journal2022.bib}
\addbibresource{publications/journal2021.bib}
\addbibresource{publications/journal2020.bib}
\addbibresource{publications/journal2019.bib}
\addbibresource{publications/journal2018.bib}
\addbibresource{publications/journal2017.bib}
\addbibresource{publications/conference2022.bib}
\addbibresource{publications/conference2021.bib}
\addbibresource{publications/conference2020.bib}
\addbibresource{publications/conference2019.bib}
\addbibresource{publications/conference2016.bib}
\addbibresource{publications/conference2015.bib}
\usepackage{refcount}
\DeclareNameAlias{author}{last-first}
\defbibenvironment{bibliography}
{\list
	{\printtext[labelnumberwidth]{%
			\printfield{labelprefix}%
			\printfield{labelnumber}}}
	{\setlength{\labelwidth}{\labelnumberwidth}%
		\setlength{\leftmargin}{5em}%
		\setlength{\labelsep}{\biblabelsep}%
		\addtolength{\leftmargin}{\labelsep}%
		\addtolength{\leftmargin}{\leftskip}%<----- here
		\setlength{\itemsep}{\bibitemsep}%
		\setlength{\parsep}{\bibparsep}}%
	\renewcommand*{\makelabel}[1]{\hss##1}}
{\endlist}
{\item}
\renewbibmacro{in:}{}
\renewcommand{\finentrypunct}{}

%----------------------------------------------------------------------------------
%            personal data
%----------------------------------------------------------------------------------
\firstname{Vatsal}
\familyname{Sanjay}
\title{Ph.D.}
\address{ Fluid Dynamicist}{Physics of Fluids}{University of Twente}
%\mobile{+31-7895940240}
%\email{vatsalsanjay@gmail.com}
\homepage{vatsalsanjay.com}
\social{vatsalsanjay}
\social[twitter][twitter.com/VatsalSanjay]{@VatsalSanjay}
\social[github][github.com/VatsalSy]{VatsalSy}

%\quote{\textbf{On a quest in the world of multi-phase flows}}
\usepackage{lastpage}
\rfoot{\textit{\small{\color{gray}\thepage/\color{red}\pageref{LastPage}}}}
\defbibnote{weblink}{To access the full-texts, please visit \href{https://www.vatsalsanjay.com/publications}{\color{cyan}\textbf{\underline{my web page}}}.}
\begin{document}
\hypersetup{
	colorlinks,
	linkcolor={red!50!black},
	citecolor={blue!50!black},
	urlcolor={blue}
}
%-----       resume       ---------------------------------------------------------
\makecvtitle
\cvitem{Updated On:}{\today}

\section{\textbf{Education}}
\cventry{\textbf{2018--2022}}{Ph.D. (Fluid Dynamics)}{}{}{}{Physics of Fluids, University of Twente}
\cvitem{Thesis}{\textit{Viscous free-surface flows}, \href{https://doi.org/10.3990/1.9789036554077}{DOI: 10.3990/1.9789036554077}}
%\cvitem{}{\href{https://doi.org/10.3990/1.9789036554077}{DOI: 10.3990/1.9789036554077}}
%\cvitem{Focus on:}{Volume of Fluid simulations, Drop Impact, Viscoplastic flows, Three phase flows}
\cvitem{Graduated}{Doctor cum laude (met Lof): with distinction.}

\cventry{\textbf{2013--2018}}{B.Tech (Mechanical Engineering) \& M.Tech (Thermal Engineering)}{}{}{}{Two-Phase Flow \& Instability Lab, Indian Institute of Technology Roorkee.}
\cvitem{Thesis}{\textit{Understanding of mutual interactions between liquid jets: Entrainment and sheet formation}, \href{https://goo.gl/kws3Nf}{https://goo.gl/kws3Nf}}
%\cvitem{}{\href{https://goo.gl/kws3Nf}{https://goo.gl/kws3Nf}}
%\cvitem{Focus on:}{Liquid Jet Dynamics, Formation \& Stability of Liquid Chain,  Multiscale Numeical Simulations, Flame Dynamics}

\cvitem{Graduated}{First Division with Distinction (CGPA:\textit{ 9.10/10}).}
\cventry{\textbf{2013}}{AISSCE (High School)}{}{graduated with \textit{96.4\%} marks.}{}{}
%\cventry{\textbf{2011}}{AISSE}{Secondary School}{Graduated with CGPA of \textit{10/10}}{}{}

\section{\textbf{Professional Experience}}
\cventry{Now}{Postdoctoral researcher}{\href{https://pof.tnw.utwente.nl/people/profile/1330}{Physics of Fluids group}}{}{}{with \href{https://en.wikipedia.org/wiki/Detlef_Lohse}{Prof. Detlef Lohse} at University of Twente, Enschede, the Netherlands.}
%\cventry{2022 -- Present}{Postdoctoral researcher}{\href{https://pof.tnw.utwente.nl/people/profile/1330}{Physics of Fluids group}}{}{}{University of Twente, Enschede, the Netherlands}
%\cvitem{\textbf{Advisor:}}{\href{https://en.wikipedia.org/wiki/Detlef_Lohse}{\textbf{Prof. Detlef Lohse}}}

%\cventry{2018 -- 2022}{Researcher (Ph.D. Candidate)}{\href{https://pof.tnw.utwente.nl/people/profile/1330}{Physics of Fluids group}}{}{}{with \href{https://en.wikipedia.org/wiki/Detlef_Lohse}{Prof. D. Lohse} at University of Twente, Enschede, the Netherlands}

\cventry{May -- July, 2016}{Research Intern}{\href{http://lmfa.ec-lyon.fr/}{Fluid Mechanics \& Acoustics Laboratory - UMR 5509}}{}{}{with \href{http://lmfa.ec-lyon.fr/spip.php?article408}{Prof. Jean-Philippe Matas},
	\href{http://lmfa.ec-lyon.fr/spip.php?article378}{Prof. J. John Soundar Jerome}, \& \href{http://www.ens-lyon.fr/PHYSIQUE/presentation/annuaire/bourgoin-mickael}{Prof. Micka\"el Bourgoin} at Universit\'e Claude Bernard Lyon 1, France.}
%\cvitem{\textbf{Advisors:}}{
	%	\textbf{\href{http://lmfa.ec-lyon.fr/spip.php?article408}{Prof. Jean-Philippe Matas},
		%		\href{http://lmfa.ec-lyon.fr/spip.php?article378}{Prof. J. John Soundar Jerome}, \href{http://www.ens-lyon.fr/PHYSIQUE/presentation/annuaire/bourgoin-mickael}{Prof. Micka\"el Bourgoin}}
	%}
\cventry{2014 -- 2018}{Research Assistant}{\href{http://twophaseiitr.weebly.com/}{Two-Phase Flow \& Instability Lab}}{}{}{with \href{https://www.iitr.ac.in/departments/ME/pages/People+Faculty+akdasfme.html}{Prof. Arup Kumar Das} at Indian Institute of Technology Roorkee, India.}
%\cvitem{\textbf{Advisor:}}{\href{https://www.iitr.ac.in/departments/ME/pages/People+Faculty+akdasfme.html}{\textbf{Prof. Arup Kumar Das}}}

%\pagebreak
\section{\textbf{Theses Supervised}}
\cvitem{Masters}{\href{https://bit.ly/3NG2fpz}{Tom Appleford}, \href{https://bit.ly/3h6Z26e}{Steven Meuleman}}
\cvitem{Bachelors}{\href{https://bit.ly/3Up7xIw}{Twan Heijink}, \href{https://bit.ly/3Ta5Nl1}{Thijmen Kroeze}, \href{https://bit.ly/3zPPnHH}{Coen Verschuur}, \href{https://bit.ly/3fFODhz}{Pim Dekker}, \href{https://bit.ly/3hbTCHb}{Laurence Bruggink}}

\section{\textbf{Peer Review Contributions}}
\cvitem{Referee for}{J. Fluid Mech. (40), Phys. Rev. Lett. (4), Phys. Rev. Fluids (1), Phys. Rev. E (2), Droplet (2), among others.}

%\section{\textbf{Teaching}}
%\subsection{\textbf{Advanced Fluid Mechanics}}
%\cvitem{2018-Now}{Teaching Assistant
%	\begin{itemize}
%		\item
%\end{itemize}}
\section{\textbf{Awards \& Achievements}}
\cventry{2022}{\textbf{Doctor cum laude}}{met Lof (with distinction)}{University of Twente.}{}{}
\cventry{2018}{\textbf{Department gold medal}}{}{Indian Institute of Technology Roorkee.}{}{}
\cventry{2017}{\textbf{All India Rank 2988}}{GATE}{among 190648 candidates.}{}{}
\cventry{2015}{\textbf{Summer Undergraduate Research Award}}{}{Indian Institute of Technology Roorkee.}{}{}
%\cvitem{}{Awarded summer fellowship for two months long research project}
\cventry{2013}{\textbf{All India Rank 1512}}{JEE Advanced, India}{in top 1\% of the total appearing students.}{}{}
\cventry{2013}{\textbf{All India Rank 765}}{JEE Mains, India}{Percentile score of 99.8\%.}{}{}
\cventry{2013}{\textbf{City Rank 1}}{AISSCE (High School)}{highest score in the district of Darbhanga.}{}{}
%\section{\textbf{Technical Skills}}
%\cvdoubleitem{\textbf{CFD:}}{Gerris, Basilisk C, LAMMPS-SPH \& MD, PARIS Simulator, Fire Dynamics Simulator, OpenFOAM, ANSYS-Fluent} {\textbf{Lab based:}}{LabView: Voltage \& current module, Conductivity \& optical probes, High speed camera imaging \& image processing}
%\cvdoubleitem{\textbf{Languages:}}{C, C++, MATLAB, Python, \LaTeX} {\textbf{Others:}}{Octave, SolidWorks, AutoCAD}
\section{\textbf{Scientific Outreach}}
\cvitem{2020-Present}{Twitter account for Physics of Fluids group, \href{https://twitter.com/poftwente}{@poftwente}.}
\cvitem{2020-Present}{Physics of fluids group seminar organizer.}
\cvitem{2022-Present}{Skype a Scientist.}
\cvitem{2022-Present}{Physicist To-Go.}
\cvitem{2022-Present}{APS-DFD peer mentoring program (as a mentor).}
\cvitem{2021}{Panel discussion on \href{https://www.vatsalsanjay.com/talks/fluiddynamicsfuture}{Future of fluid dynamics}}
\cvitem{2021}{Panel discussion on \href{https://www.vatsalsanjay.com/talks/let-us-talk-research}{Research \& higher education}}
%\subsection{\textbf{Skype a Scientist}}
%\cvitem{Oct, 2022}{Prairie Home School}
%\subsection{\textbf{Physicist To-Go}}
%\cvitem{Jan, 2022}{}

\section{\textbf{Invited Talks}}
\subsection{\textbf{Impact of droplets}}
\cvitem{Jan, 2023}{\begin{itemize}
		\item Universit\'e Claude Bernard Lyon 1, France.
		\item Indian Institute of Technology Delhi.
\end{itemize}}
\vspace*{-4mm}
\cvitem{Dec, 2022}{Indian Institute of Technology Bombay.}
\cvitem{Oct, 2022}{\begin{itemize}
		\item University of Akron (Virtual).
		\item \href{https://youtu.be/enTMAucwUDs}{Complex Fluids and Soft Matter (CFSM) Seminar Series} (Virtual).
\end{itemize}}
\vspace*{-4mm}
\subsection{\textbf{Taylor-Culick Retractions}}
\cvitem{Dec, 2022}{\begin{itemize}
		\item Indian Institute of Technology Roorkee.
		\item Indian Institute of Technology Kharagpur.
\end{itemize}}
\vspace*{-4mm}
\subsection{\textbf{Bouncing \& Jumping Drops \& Bubbles}}
\cvitem{Jan, 2023}{Indian Institute of Technology Patna.}
\subsection{\textbf{Interactions of Liquid Jets}}
\cvitem{Jan, 2018}{Physics of Fluids, University of Twente, Enschede, the Netherlands.}
\cvitem{Mar, 2017}{Cognizance Technical Festival, Indian Institute of Technology Roorkee.}
\cvitem{Jul, 2016}{Universit\'e Claude Bernard Lyon 1, France.}
\subsection{\textbf{Physics \& Computations}}
\cvitem{2014-2017}{MIESS, Indian Institute of Technology Roorkee.}

\section{\textbf{Research Interests}}
\cvitem[-1em]{\textbf{Fluid}}{
	\hspace{-25mm}\cvlistdoubleitem{Multiphase flows}{Non-Newtonian flows}
	\hspace{-25mm}\cvlistdoubleitem{Drops}{Bubbles}
	%	\hspace{-25mm}\cvlistdoubleitem{Jets}{Sheets}
	\hspace{-25mm}\cvlistdoubleitem{Liquid Jets \& their Interactions}{Liquid sheets: formation \& stability}
	\hspace{-25mm}\cvlistdoubleitem{Computational multi-fluid dynamics}{Interface reconstruction}
}
\cvitem[-1em]{\textbf{Fire}}{
	\hspace{-25mm}\cvlistdoubleitem{Compartmental fire}{Fire propagation and soot flow}
}

%\pagebreak
\nocite{*}
\defbibheading{bibliography}{}
%\section{\textbf{Manuscripts in Preparation or Under Review}}
%\section{\textbf{Manuscripts under review}}
%\printbibliography[prenote=weblink,keyword=JournalReview,resetnumbers=true]
\section{\textbf{Publications}}
\printbibliography[prenote=weblink,keyword=Journal,resetnumbers=true]
%%\pagebreak
\section{\textbf{Contributed Conference Presentations}}
\printbibliography[prenote=weblink,keyword=Conference,resetnumbers=true]
\end{document}
